\bf Service Chain Placement in SDNs \thanks{ A preliminary version appeared in the 3rd International Workshop on Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017. Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2018-07-22 src/chain.tex
dror

Given a directed acyclic graph $G = (V,E)$, let $\pi:V \to [n]$ be an
arbitrary topological ordering of the vertices in $G$.  We transform
$G$ into a layered DAG $G'$ by replacing every edge $(v,u) \in E$ with
a directed path of length (number of edges) $\pi(u) - \pi(v)$ from $u$
to $v$.
%
Figure~\ref{fig:layer-transform}.  depicts this process.  It is
straightforward to see that the resulting graph $G'$ is indeed a
layered DAG.

@@

The algorithm uses dynamic programming.  We find the optimal 2-robust
placement for every combination of two physical vertices from the same
layer, and every combination of two virtual edges.
%
Formally, we define $\ft((\alpha_1,\zeta_1), (\alpha_2,\zeta_2), v_1,
v_2)$ to be the minimum cost 2-robust placement of two service chains
that start at $\sigma$ and end with the edges $(\alpha_1,\zeta_1)$ and
$(\alpha_2,\zeta_2)$, respectively, such that a virtual paths from
$\sigma$ to $\alpha_1$ and $\alpha_2$ are placed into internal vertex
disjoint physical paths that start at $s$ and end at $v_1$ and $v_2$,
respectively.
%
We remaind that $\cost^i_{v_i}(\gamma_i,\beta_i)$ is the cost, with respect to
$c_i$, of a minimum cost path from $\gamma_i$ to $\beta_i$ whose total
processing requirement can be handled by $v_i$.  
Consider the following recursive definition:
\[
\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),s,s)
= \cost^1_{s}(\sigma \leadsto \alpha_1) + \cost^2_{s}(\sigma \leadsto \alpha_2) 
\]
otherwise, for $v_1 \neq v_2$, where $v_1$ and
$v_2$ in the same layer, we have
\[
\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),v_1,v_2)
=
\min\set{
%
\begin{array}{l}
\ft((\gamma_1,\beta_1),(\gamma_2,\beta_2),u_1,u_2) \\ 
+ \cost^1_{v_1}(\beta_1 \leadsto \alpha_1) \\
+ \cost^2_{v_2}(\beta_2 \leadsto \alpha_2)
\end{array}
}
\]

Where we take the minimum over all the possible virtual functions and
physical nodes such that:

\begin{itemize}
  \item $\gamma_i \preceq \alpha_i$
  \item $\beta_i \preceq \alpha_i \lor \beta_i = \zeta_i$ 
  \item $(\gamma_i,\beta_i) \in \calE$
  \item $u_1 \neq u_2 \lor u_1 = u_2 = s$
  \item $(u_i,v_i) \in E$
  \item $b(\gamma_i,\beta_i) \leq b(u_i,v_i)$
\end{itemize}

@@

The running time is polynomial, since there is a polynomial number of
states and the computation of $\cost^i_{v_i}(\gamma_i,\beta_i)$ can be
done in polynomial time, as shown in
Section~\ref{sec:chain-placement}.  The above algorithm computes the
cost of an optimal $2$-robust placement, and as usual, one may compute
an optimal $2$-robust placement using stanard techniques.

@@

\clearpage

>>>>

Given a directed acyclic graph $G = (V,E)$, let $\pi:V \to [n]$ be an
arbitrary topological ordering of the vertices in $G$.  We transform
$G$ into a layered DAG $G'$ by replacing every edge $(v,u) \in E$ with
a directed path of length (number of edges) $\pi(u) - \pi(v)$ from $u$
to $v$.
%
Figure~\ref{fig:layer-transform} depicts this process.  It is
straightforward to see that the resulting graph $G'$ is indeed a
layered DAG.

@@

The algorithm uses dynamic programming.  We find the optimal 2-robust
placement for every combination of two physical vertices from the same
layer, and every combination of two virtual edges.
%
Formally, we define $\ft((\alpha_1,\zeta_1), (\alpha_2,\zeta_2), v_1,
v_2)$ to be the minimum cost 2-robust placement of two service chains
that start at $\sigma$ and end with the edges $(\alpha_1,\zeta_1)$ and
$(\alpha_2,\zeta_2)$, respectively, such that a virtual paths from
$\sigma$ to $\alpha_1$ and $\alpha_2$ are placed into internal vertex
disjoint physical paths that start at $s$ and end at $v_1$ and $v_2$,
respectively.
%
Recall that $\cost^i_{v_i}(\gamma_i,\beta_i)$ is the cost, with
respect to $c_i$, of a minimum cost path from $\gamma_i$ to $\beta_i$
whose total processing requirement can be handled by $v_i$.
%
Consider the following recursive definition.  First,
\[
\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),s,s)
= \cost^1_{s}(\sigma \leadsto \alpha_1) +
  \cost^2_{s}(\sigma \leadsto \alpha_2)
~.
\]
Otherwise, for $v_1 \neq v_2$, such that $v_1, v_2 \in L_i$, for some
$i$, we have
\[
\ft((\alpha_1,\zeta_1),(\alpha_2,\zeta_2),v_1,v_2)
=
\min\set{
%
\begin{array}{l}
\ft((\gamma_1,\beta_1),(\gamma_2,\beta_2),u_1,u_2) \\ 
+~ \cost^1_{v_1}(\beta_1 \leadsto \alpha_1) 
+~ \cost^2_{v_2}(\beta_2 \leadsto \alpha_2)
\end{array}
}
\]
where we take the minimum over all the possible virtual functions
$\gamma_1, \beta_1, \gamma_2, \beta_2$ and physical nodes $u_1, u_2$,
such that:
\begin{itemize}
  \item $\gamma_i \preceq \alpha_i$,
  \item $\beta_i \preceq \alpha_i$ or $\beta_i = \zeta_i$,
  \item $(\gamma_i,\beta_i) \in \calE$,
  \item $u_1 \neq u_2$ or $u_1 = u_2 = s$,
  \item $(u_i,v_i) \in E$, and
  \item $b(\gamma_i,\beta_i) \leq b(u_i,v_i)$
\end{itemize}

@@

The running time is polynomial, since there is a polynomial number of
states and the computation of $\cost^i_{v_i}(\gamma_i,\beta_i)$ can be
done in polynomial time, as shown in
Section~\ref{sec:chain-placement}.  The above algorithm computes the
cost of an optimal $2$-robust placement, and as usual, one may compute
an optimal $2$-robust placement using standard techniques.

@@
